Discrete Quantum Theories and Computing

### 2019-02-11 dissertation.tex
dissertation.lyx Acknowledgments Updates...

To have the current the content of the dissertation, I would also
like to thank John Gardiner for some inspiring discussion about quantum
probability measures over finite fields~\cite{Gardiner2014}. His
research supervised by Prof.\ Gerardo Ortiz inspired Sec.~\ref{subsec:Maximal-entanglement}
and~\ref{sec:Toward-IVPM}. Besides of my committee members, the
knowledge I learned from teachers in other courses help me consolidate
this dissertation as listed in Table~\ref{tab:teacher}. Although
not directly relating to the dissertation, I have to thank for your
teaching to make me more mature and easier to communicate with others,
especially my English teachers, Traci Nagle, Elizabeth ``Betsy''
Merceron, and Kexin ``Casey'' Chen (谌可心).
\begin{table}[t]
\begin{doublespace}
\noindent \centering{}\caption{\label{tab:teacher}The knowledge I learned from teachers in other
courses help me consolidate this dissertation, where IUB stands for
Indiana University Bloomington and NTU stands for National Taiwan
University.}
%% ERT block 1 (before LyX tabular)
\renewcommand{\tabular}{\tabularx{\linewidth}}
\renewcommand{\endtabular}{\endtabularx} 
\begin{tabular}{M{Jin-Tzu~Chen}cM{MATH-M522}Y}
\toprule 
Instructor & School & Course & Relation with the dissertation\tabularnewline
\midrule
\midrule 
Tom Lewis & IUB & SLST-T501 & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
paper of \emph{Academic Writing}.\tabularnewline
\midrule 
Michael\nolinebreak[3] A. Mandell & IUB & MATH-M522 & The textbook~\cite{Hatcher2001} of \emph{Topology II} is cited
in Chapters~\ref{chap:Introduction} and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline
\midrule 
Steven Myers & IUB & CSCI-B502 & The textbook~\cite{AroraBarak2009} of \emph{Computational Complexity}
is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline
\midrule 
Valery Lunts & IUB & MATH-M501 & The textbook~\cite{DummitFoote2004} of \emph{Survey of Algebra}
is cited in Sec.~\ref{sec:background}, \ref{discretequantumtheoryI},
and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
\midrule 
Huah Chu\linebreak[3] (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & The textbook~\cite{Artin1991} of \emph{Algebra (I)} and \emph{(II)}
is cited in Sec.~\ref{CQC1qubitBloch.sec}, \ref{sec:background},
\ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
\midrule
Jin-Tzu Chen\linebreak[3] (陳金次) & NTU & 201~31300 & The textbook~\cite{GAMELIN2003} of \emph{Functions of a Complex Variable}
is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline
\bottomrule
\end{tabular}% ERT block 2 (after LyX tabular)
\renewcommand{\tabular}{\ORIGtabular}
\renewcommand{\endtabular}{\ORIGendtabular} 
\end{doublespace}
\end{table}

Many people have done everything to make my double-major smooth and
to financially support me during my Ph.D. study. I need to thank all
of them, and the complete list of the support according to the employment
and award is listed in my Curriculum Vitae at the end of the dissertation.
Most importantly Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
helped me deal with the rules, supervised my reading courses for writing
our papers, and financially support me as a research assistant and
associate. In the department of Mathematics, I need to thank the graduate
services assistant, Kate Forrest, and the directors of graduate study
in Mathematics, especially Prof.\ Christopher Judge, Prof.\ Matthias
Weber, and Prof.\ Michael A.\ Mandell. In the department of Computer
Science, I want to thank the graduate student office; the director
of AI/UI assignments, Charles Pope; the directors of Ph.D. study in
Computer Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
Ergun}; the infrastructure and technology group (ITG). In particular,
I don't know how much computational power I consumed to count the
states in Sec.~\ref{subsec:Maximal-entanglement}. These computational
power not only came from the Linux systems in Computer Science but
also came from the Big Red II administrated by the University Information
Technology Services (UITS). Also, I have checked out a stack of books
from the Indiana University Libraries. While the books are not in
the collection, I occasionally requested them via the Interlibrary
Loan service, submitted the Purchase Recommendation Form to suggested
IU libraries to buy them.\todo{Acknowledgments cleaned up until here.
}

Except the financial support via employment and award, I have also
support by my family, especially my father Cheng-Tien Tai (戴振沺).

Others who help me indirectly on the content of the dissertation including
Kin Wai Chan, Weihua Liu (刘伟华), Caren Liu (劉鈺平), Meng-Wei Chen
(陳孟瑋), Hao-Chun Lee (李浩君), Chao-Hong Chen (陳昭宏)\ldots , etc. This
could be listed on and on. I still thank you even if your name is
not listed here, and sorry for my bad memory.

Thank all my friends for your support, including:

@@

\item Meng-Wei Chen (陳孟瑋) as my roommate, AT\&T family plan member,
and emergency contact for all kinds of emergency and non-emergency
situations.

@@

\item Hao-Chun Lee (李浩君) and Hsien-Ching Kao (高憲慶) for discussing
what I did from the perspective of a general PhD. in Physics and working
later in more computational industry.

@@

Finally, I thank Jin-Ru Yang (楊謹如) for everything that could not be
written here.\end{acknowledgments*}

>>>>

To have the current the content of the dissertation, I would also
like to thank John Gardiner for some inspiring discussion about quantum
probability measures over finite fields~\cite{Gardiner2014}. His
research supervised by Prof.\ Gerardo Ortiz inspired Sec.~\ref{subsec:Maximal-entanglement}
and~\ref{sec:Toward-IVPM}. Besides of my committee members, what
I learned from the teachers in other courses also helped me consolidate
this dissertation as listed in Table~\ref{tab:teacher}. Even if
what taught by my other teachers are not directly related to this
dissertation, I have to thank for your teaching to make me more mature
and easier to communicate with others, especially my English teachers,
Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
Chen (谌可心).
\begin{table}[t]
\begin{doublespace}
\noindent \centering{}\caption{\label{tab:teacher}Other courses I took which is relevant to this
dissertation, where IUB stands for Indiana University Bloomington
and NTU stands for National Taiwan University.}
%% ERT block 1 (before LyX tabular)
\renewcommand{\tabular}{\tabularx{\linewidth}}
\renewcommand{\endtabular}{\endtabularx} 
\begin{tabular}{M{Jin-Tzu~Chen}cM{MATH-M522}Y}
\toprule 
Instructor & School & Course & Relation with the dissertation\tabularnewline
\midrule
\midrule 
Tom Lewis & IUB & SLST-T501 & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
paper of \emph{Academic Writing}.\tabularnewline
\midrule 
Michael\nolinebreak[3] A. Mandell & IUB & MATH-M522 & The textbook~\cite{Hatcher2001} of \emph{Topology II} is cited
in Chapters~\ref{chap:Introduction} and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline
\midrule 
Steven Myers & IUB & CSCI-B502 & The textbook~\cite{AroraBarak2009} of \emph{Computational Complexity}
is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline
\midrule 
Valery Lunts & IUB & MATH-M501 & The textbook~\cite{DummitFoote2004} of \emph{Survey of Algebra}
is cited in Sec.~\ref{sec:background}, \ref{discretequantumtheoryI},
and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
\midrule 
Huah Chu\linebreak[3] (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & The textbook~\cite{Artin1991} of \emph{Algebra (I)} and \emph{(II)}
is cited in Sec.~\ref{CQC1qubitBloch.sec}, \ref{sec:background},
\ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
\midrule
Jin-Tzu Chen\linebreak[3] (陳金次) & NTU & 201~31300 & The textbook~\cite{GAMELIN2003} of \emph{Functions of a Complex Variable}
is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline
\bottomrule
\end{tabular}% ERT block 2 (after LyX tabular)
\renewcommand{\tabular}{\ORIGtabular}
\renewcommand{\endtabular}{\ORIGendtabular} 
\end{doublespace}
\end{table}

Many people have done everything to make my double-major smooth and
to financially support me during my Ph.D. study. I need to thank all
of them, and the complete list of the support according to the employment
and award is listed in my Curriculum Vitae at the end of the dissertation.
Most importantly, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
helped me deal with the rules, supervised my reading courses for writing
our papers, and financially support me as a research assistant and
associate. In the department of Mathematics, I need to thank the graduate
services assistant, Kate Forrest, and the directors of graduate study
in Mathematics, especially Prof.\ Christopher Judge, Prof.\ Matthias
Weber, and Prof.\ Michael A.\ Mandell. In the department of Computer
Science, I want to thank the graduate student office; the director
of AI/UI assignments, Charles Pope; the directors of Ph.D. study in
Computer Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
Ergun}; and the infrastructure and technology group (ITG). In particular,
I don't know how much computational power I consumed to count the
states in Sec.~\ref{subsec:Maximal-entanglement}. These computational
power not only came from the Linux systems in Computer Science but
also came from the Big Red II administrated by the University Information
Technology Services (UITS). The Indiana University Libraries was also
extremely helpful during my dissertation research. Except for a stack
of books I checked out directly, while the books are not in their
collection, I occasionally requested them via the Interlibrary Loan
service, submitted the Purchase Recommendation Form to suggested IU
libraries to buy them.\todo{Acknowledgments cleaned up until here.
}

Except the financial support via employment and award, I have also
support by my family, especially my father Cheng-Tien Tai (戴振沺). He
always thinks one-step ahead and cares about my future more than I
do. Discussion with other family members and friends also helped me
to compose this dissertation or to do research in general. In particular,
I want to thank Prof.~Daniel Leivant, Prof.~Paul Purdom, Weihua
Liu (刘伟华), and classifies others as the following:\footnote{I only provide the Chinese name for some of them since I only know
their Chinese names and there is no unique way to alphabetize Chinese
into English. Hence, if I randomly choose a way to alphabetize their
name, it might just be a random string which might not be their English
name when they really want to use an English name. For the reader
who don't know Chinese, their names should be able to be copied directly
since the output of \XeLaTeX should be encoded in the Unicode.}

@@

\item The Ph.D. students in Mathematics, including, Kin Wai Chan,
ChunHsien Lu (呂俊賢), Cong Zhou (周蔥), Junyan Xu (许俊彦), Zhipeng Lu (路志鹏),
Robert Rose, Neal Coleman, Dami Lee, Ruiyu Yang (杨瑞雨), Yingwei Li
(李盈伟), Yu-Yuan Chen (陳裕元)\ldots{} etc.

\item My other family members, including, my mother Feng-Ming Chang
(張鳳鳴), my grandmother 戴許玉婷, my sister Sih-Sian Tai (戴司嫻), my cousins
Caren Liu (劉鈺平) and Kiwi Liu (劉子綺), \ldots{} etc.

\item My official and nonofficial roommates, including Meng-Wei Chen
(陳孟瑋), Yu ``Larry'' Chen (陈煜), Jing-Han Liou (劉經翰), Shu-Ling Wang
(王舒齡), and Wan-Ling ``Wynnie'' Chang (張婉鈴).

\item My classmates in NTU, including, Hao-Chun Lee (李浩君), Hsien-Ching
Kao (高憲慶), 鄭維,

\item My building mates, including Chao-Hong Chen (陳昭宏)

@@

\item Hao-Chun Lee (李浩君) and for discussing what I did from the perspective
of a general PhD. in Physics and working later in more computational
industry.

@@

\ldots , etc. This could be listed on and on. I still thank you even
if your name is not listed here, and sorry for my bad memory.

Finally, I want to thank Blue Coat system for providing K9 Web Protection
to block distractive websites to keep me focus, and Jin-Ru Yang (楊謹如)
for keeping the password and helping me control myself in general.\end{acknowledgments*}
